\documentclass[12pt,article]{article}
\usepackage{fullpage}
\usepackage[top=2cm, bottom=4.5cm, left=2cm, right=2cm]{geometry}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage{lastpage}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{mathrsfs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{mdframed}
\usepackage{changepage}   % for the adjustwidth environment
\usepackage{forest} 
\usepackage{tikz}   % For graph

\usepackage{float}  % To inforce inserting images at the right place


\newcommand{\Tau}{\mathrm{T}}


% For matrix
\def\horzbar{\text{magic}}

\hypersetup{%
  colorlinks=true,
  linkcolor=blue,
  linkbordercolor={0 0 1}
}

\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.05in}

\newcommand\projnumber{1}
\newcommand\course{CS534}
\newcommand\OSUID{934370552}
\newcommand\Email{buivy@oregonstate.edu}
\newcommand\Name{Vy Bui}
\newcommand\tab[1][1cm]{\hspace*{#1}}

\pagestyle{fancyplain}
\headheight 35pt
\lhead{Implementation Assignment \projnumber}
\rhead{Oct. 7, 2022}
\lfoot{}
\cfoot{}
\rfoot{\small\thepage}
\headsep 1.5em

\newenvironment{problem}[2][Problem]
    { \begin{mdframed}[backgroundcolor=gray!20] \textbf{#1 #2} \\}
    {  \end{mdframed}}
   

% Make Rightarrow with superscript
\makeatletter
\newcommand{\xRightarrow}[2][]{\ext@arrow 0359\Rightarrowfill@{#1}{#2}}
\makeatother

\begin{document}

\begin{titlepage}
    \begin{center}
        \vspace*{4cm}

        \textbf{\Large CS534 - Machine Learning}

        \vspace{0.5cm}
 
        \textbf{\Large Implementation Assignment \projnumber{}}
 
        \vspace{1cm}

        \textbf{Group 50}

        Sebastian Mueller - 933962290

        Derek Helms - 934451909

        Vy Bui - 934370552

        \vspace{2cm}

        \textbf{Instructor: Dr. Xiaoli Fern}
        \vfill
             
        \vspace{0.8cm}
      
             
        The School of Electrical Engineering and Computer Science\\
        Oregon State University\\
             
    \end{center}
\end{titlepage}

%==============================================================================%
\textbf{PART I} \newline
\textbf{a} (35 pts) Train your model for up to 4000 iterations using direrent 
learning rates. Stop early if it has converged (training MSE changes very little) 
or diverged (training MSE increases with more iterations) before reaching 4000 
iterations. Plot the MSE as a function of iterations for each learning rate. You
can generate a single figure for all curves (excluding the diverging ones), 
using diferent colors with legends to indicate which color for what learning 
rate.

Using grid search to find a good learning rate.

\textbf{Experiments} \newline
learning\_rate, mse, result

\textbf{Notes} \newline
There are a few examples where the date of sale is before the actual selling 
date  (example, line 10 with id = 1832100030). Should we allow the negative 
number?




\end{document}
